---
title: "Assignment5"
author: "Chukwuamaka Eunice Nwaobi - 12710521"
date: "24/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Tutorial5.R")
```

# Tutorial 5

## Results and Discussion of Research

#### Although the data sample size mainly provides insight into the Asian and White demographic, this visualization of survival rates is both interesting and especially relevant considering the current political atmosphere. 
#### Interesting results arise from observation of the median survival time for these different groups:


### Analysis without p-Value & Table

#### Some race groups had high dropout/mortality rates and therefore did not proceed as far as ~3000th time interval. For the Asian population the dropout rate was the main factor for this low completion whereas for the Black or African American group, the impacts of the event were the main reasons why they did not progress as far as other groups. 
#### Additionally, those pertaining to the "others" demographic had lower median survival time, whereas black folks were reported to have a slightly higher median survival time. The White Folks being studied (215) in the majority had the highest median time. Suffice to say, this experiment would have been more conducive with real-world scenarios if participants proceeded to completion and dropout numbers were much lower. Data gathering and analysis performed on a more equally distributed sample size would have also contributed to better results.

```{r plotwopval, echo=FALSE}
  plotwopval
```

<b><ul>
### Analysis with p-Value & Table
</ul><b>

#### When observing the results with the p-table, we find that by the 4000th time interval everyone has dropped out of the experiment. White participants were observed to have endured the longest. By the 2000th time interval, we observe that only 13/166 Asians, 1/24 Black or African Americans, 18/219 Whites, and 1/15 participants belonging to the other category remained.
#### The p-Value of .34 suggests that that race is not statiscally significant and has no bearing on the survival rate. 

```{r plotwpval, echo=FALSE}
  plotwpval
```