---
title: "Tutorial 7"
author: "Chukwuamaka Eunice Nwaobi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('deliverable.R')
```


If we assume p-value of 3%, what would be the expected false positive?
```{r, echo=FALSE}
q1
```

Following (1), How many genes are there if you set FDR cutoff as % false positive in (1) lowered by ONE percent?
```{r, echo=FALSE}
q2
```
Having results from 1 & 2, list the top 5 upregulated and top 5 downregulated genes?

## Here are the genes for most significant upregulation:
```{r, echo=FALSE}
q3_up
```
## And, here are the genes for most significant downregulation:
```{r, echo=FALSE}
q3_down
```
Same as to heatmep covered in this tutorial, plot heatmap of the found genes in part (3)

Hint: Gene names should be annotated names. The Heatmap should have annotation_col. Rows should be the names of genes and columns should be sample names
```{r, echo=FALSE}
q4
```

Print the names of top upregulated and downregulated pathways?

## For the sakes of the assignment, the word 'top' was interpreted as 6.
## Here are the names for most significant upregulated pathways:
```{r, echo=FALSE}
q5_top
```
## And, here are the names for most significant downregulated pathways:
```{r, echo=FALSE}
q5_down
```